---
title: "Vaccines: Many Beliefs Pilot 4"
author: "Derek Powell"
date: "June 30, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

```{r}

filename <- "data/vb_pilot4.csv"

headers <- as.matrix(read.csv(filename, skip = 0, header = F, nrows = 1, as.is = T ))
df <- read.csv(filename, skip = 3, header = F)
colnames(df) <- headers

df <- df[which(df$Status==0),] # remove survey previews

# remove unused qualtrics variables
remove_cols <- c("RecipientLastName",
                 "RecipientFirstName",
                 "RecipientEmail",
                 "Finished",
                 "ResponseId",
                 "ExternalReference",
                 "DistributionChannel",
                 "UserLanguage",
                 "Status")

df <- df[ , -which(names(df) %in% remove_cols)]
df <- df[which(df$vaccDanger_check_3==3 & df$hb_check_5==5),]
```

```{r}
all_items <- c("hb_1",
"hb_2",
"hb_3",
"hb_4",
"nat_1",
"nat_2r",
"nat_3",
"nat_4",
"nat_5r",
"medSkept_1",
"medSkept_2r",
"medSkept_3",
"medSkept_4",
"medSkept_5r",
"diseaseRare_1",
"diseaseRare_2",
"diseaseRare_3r",
"diseaseRare_4",
"diseaseRare_5r",
"diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"vaccEff_1",
"vaccEff_2r",
"vaccEff_3r",
"vaccEff_4",
"vaccDanger_1",
"vaccDanger_2r",
"vaccDanger_3",
"vaccDanger_4r",
"vaccTox_1r",
"vaccTox_2",
"vaccTox_3",
"vaccTox_4r",
"vaccStrain_1",
"vaccStrain_2r",
"vaccStrain_3",
"vaccStrain_4r",
"vaccStrain_5",
"vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r",
"parentExpert_1",
"parentExpert_2",
"parentExpert_3",
"parentExpert_4r",
"parentExpert_5r",
"infantImmLimCap_1",
"infantImmLimCap_2r",
"infantImmLimCap_3",
"infantImmLimCap_4",
"infantImmLimCap_5r",
"infantImmWeak_1",
"infantImmWeak_2",
"infantImmWeak_3",
"infantImmWeak_4r",
"infantImmWeak_5r",
"overpar_1r",
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r",
"overpar_6r")


```


```{r}
library(ggplot2)
# df <- read.csv("vb_pilot2.csv")

reverse_items <- all_items[!sapply(
  lapply(all_items, function (x) {
  if (substr(x,nchar(x),nchar(x))=="r") {
    return(x)
  }
}), is.null)]
 
df[,reverse_items] <- lapply(df[,reverse_items], function(x) {
  8-x
})

df_main <- df[,all_items]
```



# Introduction

This is a notebook for the fourth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 1 to comprehension checks, leaving 99.

# Item Correlations

Here's a correlation matrix for all individual items. It appears items of some scales are intercorrelating well, though others are weaker. There is also considerable correlation among items across scales--as we might expect.

```{r,fig.height=9,fig.width=9}
library(corrplot)
library(viridis)

corrplot(cor(df_main),
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_main[,all_items]),
         order="hclust",
         # addrect=3,
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

# Scale Internal Consistency Reliability

# Problem scales

Below are computed chronbach's alpha for all scales along with more detailed analyses of scales that are problematic.

## Disease Severity

Disease severe is now a weaker scale. I'd wager this is due to our changes, as this used to be highly reliable at $\alpha$  = .86.

```{r}
diseaseSevere <- all_items[20:24]

diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
diseaseSevere.alpha$total$raw_alpha
diseaseSevere.alpha 

```

### Diagnosing

```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
corrplot(cor(df[,diseaseSevere]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

## Naturalism

This scale took a hit -- possibly due to the reverse coding? possibly just random variation. It went down from .825 so random variation is possible but seems on the extreme end.

```{r}
nat <- all_items[5:9]

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha
naturalism.alpha


```


## Overparenting with babies (new scale)

This got worse!

```{r}
# overPar <- all_items[62:67]
overPar <- c(
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r")

overPar.alpha <- psych::alpha(df[,overPar])

overPar.alpha
```

### Diagnosing

No clear fixes here, just not doing very well.

```{r}
ggplot(data = melt(df[,overPar]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,overPar]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

# Acceptable scales

The remaining scales are (within rounding) in the acceptable reliabiltiy range.

## Holistic Balance

This reliability is lower but this scale is unchanged (and a pre-existing scale, so we should leave it alone).

```{r}
hb <- all_items[1:4]

hb.alpha <- psych::alpha(df[,hb])
hb.alpha$total$raw_alpha
```

## Disease Rarity

```{r}
diseaseRare <- all_items[15:19]

diseaseRare.alpha <- psych::alpha(df[,diseaseRare])
diseaseRare.alpha$total$raw_alpha

```

## Vaccine Effectiveness

```{r}
vaccEff <- all_items[25:28]

vaccEff.alpha <- psych::alpha(df[,vaccEff])
vaccEff.alpha$total$raw_alpha
```

## Vaccine Danger

```{r}
vaccDanger <- all_items[29:32]

vaccDanger.alpha <- psych::alpha(df[,vaccDanger])
vaccDanger.alpha$total$raw_alpha
```

## Vaccines are toxic

```{r}
vaccTox <- all_items[33:36]

vaccTox.alpha <- psych::alpha(df[,vaccTox])
vaccTox.alpha$total$raw
```

## Medical Skepticism

This is just barely making the grade now. Removing 5r would improve the reliability. I thought the phrasing of that item was a bit awkward after reverse coding, so maybe it can be fixed. 

```{r}
medSkept <- all_items[10:14]

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
medSkept.alpha

corrplot(cor(df[,medSkept]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

## Vaccination Intentions

```{r}
vaccIntent <- all_items[42:46]

vaccIntent.alpha <- psych::alpha(df[,vaccIntent])
vaccIntent.alpha$total$raw_alpha
```


## Parental Expertise

Success! Reliability is very solid.

```{r}
parExpert <- all_items[47:51]

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
parExpert.alpha
```

Looks a little two-dimensional though. Items 4 and 5 are both about trusing doctors' advice, so I suppose it's not surprising they hang together even more strongly.

```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,parExpert]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,parExpert]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

## Infant immune system has limited capacity

Reliability is now very good.

```{r}
immCap <- all_items[52:56]

immCap.alpha <- psych::alpha(df[,immCap])
immCap.alpha$total$raw_alpha
immCap.alpha

```

## Infants' immune systems are weak

Looks good!

```{r}
immWeak <- all_items[57:61]

immWeak.alpha <- psych::alpha(df[,immWeak])
immWeak.alpha$total$raw_alpha
immWeak.alpha

```

## Vaccines strain the immune system

Now with five items this makes for a very reliable scale.

```{r}
vaccStrain <- all_items[37:41]

# cor(df$immStrain_1,df$immStrain_2r)

vaccStrain.alpha <- psych::alpha(df[,vaccStrain])

vaccStrain.alpha

```

# Scale Distributions

Here I'm computing the scale average for all scales but the "children's weak immune system" scale and the "passive immune system" scale, where I'm making the changes suggested from the reliability analysis. *UPDATE*: Now also changing the "immune system and cold symptoms" scale to remove a bad item.

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseRare <- rowMeans(df[,diseaseRare])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
# df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
# df_scales$immSympt <- rowMeans(df[,immSympt])
df_scales$immWeak <- rowMeans(df[,immWeak])
df_scales$vaccStrain <- rowMeans(df[,vaccStrain])
df_scales$vaccTox <- rowMeans(df[,vaccTox])
df_scales$overParenting <- rowMeans(df[,overPar])
```


```{r,fig.height=9,fig.width=9}
library(ggplot2)
library(reshape2)

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseRare",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parExpert",
                "immCap",
                "immWeak",
                "vaccStrain",
                "vaccTox",
                "overParenting")

# df_hist <- df_scales[,scale_vars]
plt.hist <- ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 14) + facet_wrap(~variable) + xlim(1,7)

# ggsave("scale_hists.png",plt.hist)

plt.hist
```

# Scale correlations

Here are intercorrelations among the scales (ordered by angular order of eigenvectors). I think we should use a big grain of salt interpreting any of these because this is all based on just `r nrow(df_scales)` paricipants' data. Nevertheless, let's take a look.

Some of this is expected and some is a bit surprising. Of course once we start taking into account other conditional dependencies, some of these correlations could change, or even reverse sign.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales[,scale_vars]),
         order="hclust",
         tl.cex=1.25,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```


```{r}
df_long <- df_scales
df_long$y_val <- df_long$vaccIntent
df_long <- reshape(df_long, idvar="workerId", timevar = "item", direction="long", 
             varying=list(x_val = scale_vars[-8]),
             v.names = c("x_val"))
df_long$item <- factor(df_long$item,
                       levels = seq(1,13,1),
                       labels=scale_vars[-8])

plt.scatter <- ggplot(data = df_long, mapping = aes(x = x_val, y=y_val)) + 
    geom_point(shape=1) + 
  geom_smooth(method="lm", se=FALSE, col=viridis_pal()(5)[3]) + 
  facet_wrap(~item) + 
  xlim(1,7) + ylim(1,7) + labs(y="Vaccine Intent", x="")

# ggsave("scale_scatter.png",plt.scatter)
plt.scatter
```

# Coefficient $\omega$ reliability

Coefficient $\alpha$ has a number of well-known problems, not the least of which it is often biased (either under or over-estimating). Most people who know now recommend the use of coeffiicent $\omega$, because it is unbiased and also readily interpretable: $\omega$ represents the proportion of variance in scale scores accounted for by the latent factor.

Here I'm calculating robust $\omega$ using the coefficientalpha package. A (non-robust?) implementation is also available in the psych package that relies on an SEM package. 

If $\omega$ is to be trusted it looks like the bias in $\alpha$ is leading to an underestimate of the reliability of most scales.

## Naturalism

```{r}
coefficientalpha::omega(df[,nat])
```

## DiseaseSeverity

```{r}
coefficientalpha::omega(df[,diseaseSevere])
```

## Over-parenting

Still poor.

```{r}
coefficientalpha::omega(df[,overPar])
```

## Medical skepticism

```{r}
coefficientalpha::omega(df[,medSkept])
```

## Disease Rarity

```{r}
coefficientalpha::omega(df[,diseaseRare])
```